\vspace{-1cm}\normalsize{\textbf{Fairly Random: Impact of Winning the Toss on the Probability of Winning}}

### 2016-03-07 write_up/cricket.tex
nip/tuck

\begin{center}\textbf{Abstract}\\\end{center}
In a competitive sport, every little thing matters. Yet many sports leave some large levers out of the reach of the teams, in the hands of fate. In cricket, world's second most popular sport by some measures \footnote{See \citet{Economist2011} in The Economist.}, one such lever---the toss---has been subject to much recent attention. Using a large novel dataset of 44,224 cricket matches, we estimate the impact of winning the toss on the probability of winning. The data suggest that winning the toss increases the chance of winning by a small ($\sim$ 2.8\%) but significant margin. The advantage varies heftily and systematically, by how closely matched the competing teams are, and by playing conditions---tautologically, winning the toss in conditions where the toss grants a greater advantage, for e.g., in day and night matches, has a larger impact on the probability of winning.  
\clearpage

>>>>

\begin{center}\textbf{Abstract}\\\end{center}
In a competitive sport, every little thing matters. Yet, many sports leave some large levers out of the reach of the teams, and in the hands of fate. In cricket, world's second most popular sport by some measures, \footnote{See \citet{Economist2011} in The Economist.} one such lever---the toss---has been subject to much recent attention. Using a large novel dataset of 44,224 cricket matches, we estimate the impact of winning the toss on the probability of winning. The data suggest that winning the toss increases the chance of winning by a small ($\sim$ 2.8\%) but significant margin. The advantage varies heftily and systematically, by how closely matched the competing teams are, and by playing conditions---tautologically, winning the toss in conditions where the toss grants a greater advantage, for e.g., in day and night matches, has a larger impact on the probability of winning.  
\clearpage
